Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-10-08 manuscript.Rmd
note again that we diviated from the preregistration

The last thing we need to do is to report our results with the combination of the functions `planned_analysis()` and `report_analysis()`.

@@

>>>>

Naturally we did not access the data when we wrote this code initially.
We therefore did not know is the exact format the data would have.
So we did need to change our preregistration after accessing the data to include i.a. the recoding of gender (lines 17-22) and the items (lines 23-26).
We invite the reader to evaluate the changes we made to the preregistratered code on [GitHub](https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b).

The last thing we need to preregister is the reporting of our results with the combination of the functions `planned_analysis()` and `report_analysis()`.

@@

```{r, eval=FALSE, echo=-1}
# this is a fake chunk, the faked output comes the chunk below
report_analysis(planned_analysis(simulate_data(900, 8, 0.3, 10)
```
